The globular cluster system of the Auriga simulations

### 2020-04-09 response_to_referee.tex

\section*{Comments for each section}
\subsection*{Introduction}
\begin{itemize}
\item Item
\end{itemize}

\subsection*{Sect. 2 -}
\begin{itemize}
\item We added the halo mass range of the Auriga simulations.
\item The last paragraph should now make more sense after updating the introduction.
\end{itemize}

\subsection*{Sect. 3 -}
\begin{itemize}
\item We added references to section 3.3, 3.4, and 3.5 in the first paragraph of section 3.
\item Section 3.2 has been restructured.
\item We removed the standard error on the mean and replaced `dispersion' 
by `standard deviation' in section 3.3.
\item We added a sentence to clarify the last statement in section 3.4.
\end{itemize}

\subsection*{Sect. 4 -}
\begin{itemize}
\item We added the mean number of GC candidates compared to the mean number of
star particles in the Auriga L4 galaxies. In addition, Figure 3 now shows the 
number of star particles included in the subset.
\item We clarified at various places whether we mean the mean or median among
the simulations, or if we refer to the absolute value of one of the galaxies.
\item Figure 4 - now has a vertical line to indicate the metallicity cut 
between metal-poor and metal-rich GC subpopulations in the Milky Way.
\item
\item We now show the median instead of the mean for the galactocentric radius in
section 4.2 and Figure 6.
\item Figure 6: no changes were made for rescaling the galaxies (i.e. we still
use the virial radius)
\item Figure 5 and 7: shaded regions now show the 25-75th percentiles.
\item Figure 9: The values are removed from the masked upper right corner bins.
\item Figure 2,8,9: The values of the upper and right axes have been removed from
Figure 2 and 9 (observations) for clarity (rather than the suggestion to add 
axis labels and units). However, we did not mask these bins for Figure 8 (Auriga)
because it illustrates our finding that the simulations produce a considerable
amount of mass in GC candidates with low metallicities at large radii.
\end{itemize}

### 2020-04-09 AurigaGCS.tex
Show the median of the galactocentric radius in section 4.2 and Figure 6

Throughout our analysis we compare distributions of age-selected GC 
candidates (age $>10$~Gyr) with those of all star particles (i.e.
when no additional selection criterion is applied). We further split the GC
candidates into an {\it in~situ} subset (defined as GC candidates that are 
bound to the most-massive halo/subhalo in the first snapshot that the particle 
was recorded), and an accreted subpopulation (those that have formed {\it ex~situ} and 
are bound to the most-massive halo/subhalo at $z=0$). A GC candidate either formed
{\it in~situ} or it was accreted. We consider the metallicity distribution in 
Sec.~\ref{sec:results_FeH}, the distribution of galactocentric radii in 
Sec.~\ref{sec:results_Rgc}, and the combination of both 
in Sec.~\ref{sec:results_FeHRgc}.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_obs_Au4-4_Au4-10_Au4-21-trim}.png}
    \caption{
        \emph{Top}: Metallicity distribution of the MW and M31 GCS. The solid 
        purple (magenta) line shows the GCSs of the MW (M31), and we 
        indicate the mean value with an arrow at the bottom of the x-axis. We
        overplot a double Gaussian for the MW GCS using purple dotted lines, taking
        the mean and dispersion from \citep{Harris2001}.
        \emph{Other panels}: three selected Auriga haloes as indicated in the 
        upper right corner. In each of these three panels we show the GG 
        candidates in beige, and use a beige dotted line for all star particles. 
        We split the GC candidates up into two subpopulations, those that have 
        formed {\it in~situ} (brown), and those that have been accreted (teal).
        \label{fig:Au4-10and21_FeH}
    }
\end{figure}
We select \mbox{Au4-10}\footnote{The nomenclature is `Au' for Auriga, followed by the
resolution level (4) and halo number (10, indicating which set of initial
conditions was used).}, \mbox{Au4-21}, and \mbox{Au4-4} to show the
distributions of three individual simulation runs that we consider representative
for specific behaviour, and to highlight that different runs could give rise to 
different distributions. We show the age-selected GC candidates as well as the 
accreted and {\it in~situ} subsets. The top panel of Figure~\ref{fig:Au4-10and21_FeH} shows the MW 
and M31 GCSs, where we overplot a double Gaussian for the MW GCS by 
adopting literature values of the mean $\mu$ and standard deviation $\sigma$ of 
the metal-rich and metal-poor subpopulations \citep{Harris2001}.

We find that the age cut, on average, lowers the mean metallicity $<$[Fe/H]$>$ from 
$0.0$ to $-0.6$. Furthermore, accreted GC candidates generally have lower mean 
metallicities than the {\it in~situ} subset with differences of roughly
${\sim}0.3$~dex for the majority of the simulation runs. This behaviour can be 
seen in \mbox{Au4-21}, while a slightly larger difference of ${\sim}0.5$~dex is 
seen for \mbox{Au4-10} (as plotted), \mbox{Au4-16}, \mbox{Au4-17}, \mbox{Au4-18} 
and \mbox{Au4-22}. However, this trend is reversed for \mbox{Au4-1} and \mbox{Au4-4} 
for which the {\it in~situ} subset has a lower mean metallicity instead. 
\mbox{Au4-1} is undergoing a major merger at redshift zero and we find 
$\mu = -1.51 \, ({-0.74})$ for the {\it in~situ} (accreted) GC candidates, 
although the former consists of only $1019$ particles ($1.3$\% of all GC 
candidates, and with a total mass of $5 \times 10^{7}$~M\Sun). For \mbox{Au4-4}, 
only ${10.8}$\% of the GC candidates is classified as {\it in~situ} (compared to 
{\it in~situ} fractions of ${40-80}$\% for other haloes). We note that \mbox{Au4-4}
has undergone a major merger around 2~Gyr lookback time, which is probably why
the accreted population is more metal rich. After inspection of the same figure 
for every one of the $30$~Auriga L4 haloes we find that the simulations produce
(sub)populations of GC candidates that are more metal-rich than the MW and M31 GCSs.
Moreover, none of the simulations produces GC candidates with a bimodal metallicity 
distribution.

@@

We show the mean metallicity and standard deviation of all $30$~Auriga L4 haloes
in Figure~\ref{fig:FeH_mu_sigma} to illustrate the behaviour for the full set of Auriga
galaxies. The beige crosses are to be compared to the purple and magenta cross, 
which shows the mean value of all MW and M31 GCs, respectively. In addition, we 
show the metal-rich population of the MW GCS using a solid dot, and the metal-poor
population with an open dot. We caution that
these literature values result from individual Gaussian fits to sub sets of the 
observational data cut at [Fe/H]~$= -1$. We do not include corresponding data 
points calculated using such an artificial cut for the simulated star particles.
It is interesting that the mean metallicities of the {\it in~situ} GC candidates 
appear roughly consistent with that of the metal-rich population of the MW despite 
the lack of such a metallicity cut, although the simulations show larger dispersions. 
The latter could simply be caused by the hard separation of the MW data into two 
groups, which means the range is smaller and the resulting dispersion lower. With 
regard to the M31 GCS, so far no definitive consensus has been reached
in the literature concerning uni- bi- or trimodality in the [Fe/H] distribution, 
but CR16 argues that the data, after removal of younger objects due to improved 
age classification, hints at three populations separated at [Fe/H]~$=-0.4$ and 
[Fe/H]~$ = 1.5$. None of the Auriga sub sets has a mean value that offers much 
hope that the simulated distribution is consistent with the lowest metallicity 
group in the M31 GCS. This is also true for the metal-poor population of the 
MW with a mean value of $-1.6$. The main result of this figure is 
that all Auriga L4 galaxies have metallicity distributions with (much) larger
mean values than what is observed for the MW and M31 GCS, and that we 
systematically find lower mean metallicities for the accreted GC candidates
than for those that have formed {\it in~situ}.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMFeH_withRatios-trim}.png}
    \caption{
        Mass-weighted metallicity distribution of star particles in the Auriga
        L4 simulations. We show the median value of all Auriga haloes for all
        stars (beige dotted) and GC candidates (i.e. stars with
        age $>$~10~Gyr; beige solid). The latter sub set is further split up
        between stars that formed {\it in~situ} (brown solid), and those that were accreted
        (teal solid). Shaded regions indicate the 25-75 percentile range. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:FeH}
    }
\end{figure}
We now turn to the second goal, which is to see whether sufficient total mass in 
GC candidates is produced by the Auriga simulations. To answer this question we plot
a mass-weighted metallicity distribution in Figure~\ref{fig:FeH}. We show the 
median for all $30$~Auriga L4 haloes and the 25-75 percentile range as shaded regions, 
which shows the scatter between runs that have different initial 
conditions, thus, have unique merger histories. We chose to aggregate the data 
to indicate general trends that we find when the GC candidates are split up into
the accreted and {\it in situ} subsets, rather than selecting typical examples 
of individual (simulated) galaxies. Once again we notice that the peak metallicity 
shifts down from [Fe/H]~=~$0$ to [Fe/H]~=~$-0.6$ for GC candidates compared to all stars, 
and we find that the mass at the peak lowers by roughly one dex. The mass budget 
of the GC candidates is dominated by the {\it in~situ} subpopulation above
[Fe/H]~=~$-1$, and by the accreted subset below this value. We show the MW GCS 
in purple and that of M31 in magenta, and notice that the difference between the 
MW and M31 distributions is substantially larger than the scatter between different 
Auriga galaxies, particularly around [Fe/H]~$=-1$. In addition, M31 does host 
(a handful of) GCs with [Fe/H]~$< -2.5$ as well as GCs with [Fe/H]~$ > 0$ while 
the MW does not.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{LogRgc_mu_sigma-trim}.png}
    \caption{
        Mean and standard deviation of the logarithm of radial distribution 
        of star particles in each of the $30$~Auriga L4 haloes compared to
        the MW (M31) GCS shown in purple (magenta). The Auriga (M31) radii are 
        divided by $r_{\text{vir,Au}}$ ($r_{\text{vir,M31}}$) and multiplied 
        by $r_{\text{vir,MW}}$ to compensate for different intrinsic sizes of
        the galaxies.
        \label{fig:Rgc_mu_sigma}
    }
\end{figure}
We repeat the analysis of the previous subsection for the distribution of
galactocentric radius instead of metallicity. We divide the Auriga radii by
$r_{\text{vir,Au}}$ and multiply by $r_{\text{vir,MW}}$ to compensate for the different
intrinsic sizes of the Auriga galaxies. We look for general trends present
in all Auriga L4 galaxies. Figure~\ref{fig:Rgc_mu_sigma} shows the mean and 
standard deviation of $\log_{10}(r_{\text{gal}})$ of star particles in all Auriga
L4 simulations, respectively. The purple and magenta cross again shows the mean 
of the MW and M31 GCs, which are to be compared to the beige crosses. The solid
dot now shows our calculation of the mean value of the `red' metal-rich population,
and the open dot that of the `blue` metal-poor population. We split the radii 
up into the metal-rich/metal-poor groups by taking a metallicity cut at 
[Fe/H]~=~-1 as is done in the literature.

We notice that the {\it in~situ} GC candidates are more centrally distributed, 
whereas the accreted subsets have a larger radial extent. This 
is not surprising because the classification of {\it in~situ} requires star particles 
to have formed within the virial radius, thus they could naturally be expected 
to end up at small galactocentric radii. Accreted star particles, on the other 
hand, have formed in another (sub)halo beyond the virial radius, thus, they would 
first have to migrate inwards in order to populate the innermost radii. Moreover,
we find that the simulations have a wider dispersion in $\log(r_{\text{gal}})$ than
the MW GCS, while the dispersion of M31 seems to lie within the range of dispersions
found in the Auriga galaxies. Furthermore, the mean of the MW GCS lies roughly 
within the range of values produced by the Auriga simulations, whereas the mean 
of M31 is somewhat larger and slightly closer to typical mean values of the 
accreted GC candidates in the Auriga simulations. The larger radial extent 
of the M31 GCS is generally believed to hint at a more accretion-dominated origin 
of the GCS, and may reflect a richer accretion history of M31 in comparison 
to the MW.

>>>>

Throughout our analysis we compare distributions of age-selected GC 
candidates (age $>10$~Gyr) with those of all star particles (i.e.
when no additional selection criterion is applied). The mean number of star 
particles in the Auriga L4 simulations that we select as GC candidates is 
$3.1 \cdot 10^5$ (with a mean total mass of $1.15 \cdot 10^{10}$ M$_{\odot}$), 
and the mean number of all star particles is $1.93 \cdot 10^6$ 
($7.3\cdot10^{10}$ M$_{\odot}$). The subset of GC candidates is thus around 
15\% of all the stars in the galaxy when averaged over all Auriga L4 haloes. 
We further split the GC
candidates into an {\it in~situ} subset (defined as GC candidates that are 
bound to the most-massive halo/subhalo in the first snapshot that the particle 
was recorded), and an accreted subpopulation (those that have formed {\it ex~situ} and 
are bound to the most-massive halo/subhalo at $z=0$). A GC candidate either formed
{\it in~situ} or it was accreted. We consider the metallicity distribution in 
Sec.~\ref{sec:results_FeH}, the distribution of galactocentric radii in 
Sec.~\ref{sec:results_Rgc}, and the combination of both 
in Sec.~\ref{sec:results_FeHRgc}.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_obs_Au4-4_Au4-10_Au4-21-trim}.png}
    \caption{
        \emph{Top}: Metallicity distribution of the MW and M31 GCS. The solid 
        purple (magenta) line shows the GCSs of the MW (M31), and we 
        indicate the mean value with an arrow at the bottom of the x-axis. We
        overplot a double Gaussian for the MW GCS using purple dotted lines, taking
        the mean and dispersion from \citep{Harris2001}.
        \emph{Other panels}: three selected Auriga haloes as indicated in the 
        upper right corner. In each of these three panels we show the GG 
        candidates in beige, and use a beige dotted line for all star particles. 
        We split the GC candidates up into two subpopulations, those that have 
        formed {\it in~situ} (brown), and those that have been accreted (teal).
        The numbers in parenthesis show how many star particles are included 
        in the subset.
        \label{fig:Au4-10and21_FeH}
    }
\end{figure}
We select \mbox{Au4-10}\footnote{The nomenclature is `Au' for Auriga, followed by the
resolution level (4) and halo number (10, indicating which set of initial
conditions was used).}, \mbox{Au4-21}, and \mbox{Au4-4} to show the
distributions of three individual simulation runs that we consider representative
for specific behaviour, and to highlight that different runs could give rise to 
different distributions. We show the age-selected GC candidates as well as the 
accreted and {\it in~situ} subsets. 
The top panel of Figure~\ref{fig:Au4-10and21_FeH} shows the MW 
and M31 GCSs, where we overplot a double Gaussian for the MW GCS by 
adopting literature values of the mean $\mu$ and standard deviation $\sigma$ of 
the metal-rich and metal-poor subpopulations \citep{Harris2001}.

We find that the age cut, on average, lowers the mean metallicity $<$[Fe/H]$>$ from 
$0.0$ to $-0.6$. Furthermore, accreted GC candidates generally have lower mean 
metallicities than the {\it in~situ} subset with differences of roughly
${\sim}0.3$~dex for the majority of the simulation runs. This behaviour can be 
seen in \mbox{Au4-21}, while a slightly larger difference of ${\sim}0.5$~dex is 
seen for \mbox{Au4-10} (as plotted), \mbox{Au4-16}, \mbox{Au4-17}, \mbox{Au4-18} 
and \mbox{Au4-22}. However, this trend is reversed for \mbox{Au4-1} and \mbox{Au4-4} 
for which the {\it in~situ} subset has a lower mean metallicity instead. 
\mbox{Au4-1} is undergoing a major merger at redshift zero and we find a mean
metallicity in this simulations $\mu = -1.51 \, ({-0.74})$ for the {\it in~situ} 
(accreted) GC candidates, although the former consists of only $1019$ particles 
($1.3$\% of all GC 
candidates, and with a total mass of $5 \times 10^{7}$~M\Sun). For \mbox{Au4-4}, 
only ${10.8}$\% of the GC candidates is classified as {\it in~situ} (compared to 
{\it in~situ} fractions of ${40-80}$\% for other haloes). We note that \mbox{Au4-4}
has undergone a major merger around 2~Gyr lookback time, which is probably why
the accreted population is more metal rich. After inspection of the same figure 
for every one of the $30$~Auriga L4 haloes we find that the simulations produce
(sub)populations of GC candidates that are more metal-rich than the MW and M31 GCSs.
Moreover, none of the simulations produces GC candidates with a bimodal metallicity 
distribution.

@@

We show the mean metallicity and standard deviation of all $30$~Auriga L4 haloes
in Figure~\ref{fig:FeH_mu_sigma} to illustrate the individual behaviour for the 
full set of Auriga galaxies. The beige crosses are to be compared to the purple 
and magenta cross, which shows the mean value of all MW and M31 GCs, respectively. 
In addition, we show the metal-rich population of the MW GCS using a solid dot, 
and the metal-poor population with an open dot. We caution that
these literature values result from individual Gaussian fits to sub sets of the 
observational data cut at [Fe/H]~$= -1$. We do not include corresponding data 
points calculated using such an artificial cut for the simulated star particles.
It is interesting that the mean metallicities of the {\it in~situ} GC candidates 
appear roughly consistent with that of the metal-rich population of the MW despite 
the lack of such a metallicity cut, although the simulations show larger dispersions. 
The latter could simply be caused by the hard separation of the MW data into two 
groups, which means the range is smaller and the resulting dispersion lower. With 
regard to the M31 GCS, so far no definitive consensus has been reached
in the literature concerning uni- bi- or trimodality in the [Fe/H] distribution, 
but CR16 argues that the data, after removal of younger objects due to improved 
age classification, hints at three populations separated at [Fe/H]~$=-0.4$ and 
[Fe/H]~$ = 1.5$. None of the Auriga sub sets has a mean value that offers much 
hope that the simulated distribution is consistent with the lowest metallicity 
group in the M31 GCS. This is also true for the metal-poor population of the 
MW with a mean value of $-1.6$. The main result of this figure is 
that all Auriga L4 galaxies have metallicity distributions with (much) larger
mean values than what is observed for the MW and M31 GCS, and that we 
systematically find lower mean metallicities for the accreted GC candidates
than for those that have formed {\it in~situ}.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMFeH_withRatios-trim}.png}
    \caption{
        Mass-weighted metallicity distribution of star particles in the Auriga
        L4 simulations. We show the median value of all Auriga haloes for all
        stars (beige dotted) and GC candidates (i.e. stars with
        age $>$~10~Gyr; beige solid). The latter sub set is further split up
        between stars that formed {\it in~situ} (brown solid), and those that were accreted
        (teal solid). Shaded regions indicate the 25-75 percentile range. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:FeH}
    }
\end{figure}
We now turn to the second goal, which is to see whether sufficient total mass in 
GC candidates is produced by the Auriga simulations. To answer this question we plot
a mass-weighted metallicity distribution in Figure~\ref{fig:FeH}. We show the 
median over all the $30$~Auriga L4 haloes and the 25-75 percentile range as shaded regions, 
which shows the scatter between runs that have different initial 
conditions, thus, have unique merger histories. We chose to aggregate the data 
to indicate general trends that we find when the GC candidates are split up into
the accreted and {\it in situ} subsets, rather than selecting typical examples 
of individual (simulated) galaxies. Once again we notice that the peak metallicity 
shifts down from [Fe/H]~=~$0$ to [Fe/H]~=~$-0.6$ for GC candidates compared to all stars, 
and we find that the mass at the peak lowers by roughly one dex. The mass budget 
of the GC candidates is dominated by the {\it in~situ} subpopulation above
[Fe/H]~=~$-1$, and by the accreted subset below this value. We show the MW GCS 
in purple and that of M31 in magenta, and notice that the difference between the 
MW and M31 distributions is substantially larger than the scatter between different 
Auriga galaxies, particularly around [Fe/H]~$=-1$. In addition, M31 does host 
(a handful of) GCs with [Fe/H]~$< -2.5$ as well as GCs with [Fe/H]~$ > 0$ while 
the MW does not.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{LogRgc_median_sigma-trim}.png}
    \caption{
        Median and standard deviation of the logarithm of radial distribution 
        of star particles in each of the $30$~Auriga L4 haloes compared to
        the MW (M31) GCS shown in purple (magenta). The Auriga (M31) radii are 
        divided by $r_{\text{vir,Au}}$ ($r_{\text{vir,M31}}$) and multiplied 
        by $r_{\text{vir,MW}}$ to compensate for different intrinsic sizes of
        the galaxies.
        \label{fig:Rgc_median_sigma}
    }
\end{figure}
We repeat the analysis of the previous subsection for the distribution of
galactocentric radius instead of metallicity. We divide the Auriga radii by
$r_{\text{vir,Au}}$ and multiply by $r_{\text{vir,MW}}$ to compensate for the different
intrinsic sizes of the Auriga galaxies. We look for general trends present
in all Auriga L4 galaxies. Figure~\ref{fig:Rgc_median_sigma} shows the median and 
standard deviation of $\log_{10}(r_{\text{gal}})$ of star particles in all Auriga
L4 simulations, respectively. The purple and magenta cross show the median
of the MW and M31 GCs, which are to be compared to the beige crosses. The solid
dot now shows our calculation of the median value of the `red' metal-rich population,
and the open dot that of the `blue` metal-poor population. We split the radii 
up into the metal-rich/metal-poor groups by taking a metallicity cut at 
[Fe/H]~=~-1 as is done in the literature.

We notice that the {\it in~situ} GC candidates are more centrally distributed, 
whereas the accreted subsets have a larger radial extent. This 
is not surprising because the classification of {\it in~situ} requires star particles 
to have formed within the virial radius, thus they could naturally be expected 
to end up at small galactocentric radii. Accreted star particles, on the other 
hand, have formed in another (sub)halo beyond the virial radius, thus, they would 
first have to migrate inwards in order to populate the innermost radii. Moreover,
we find that the simulations have a wider dispersion in $\log(r_{\text{gal}})$ than
the MW GCS, while the dispersion of M31 seems to lie within the range of dispersions
found in the Auriga galaxies. Furthermore, the median of the MW GCS lies roughly 
within the range of values produced by the Auriga simulations, whereas the median
of M31 is somewhat larger and slightly closer to typical median values of the 
accreted GC candidates in the Auriga simulations. The larger radial extent 
of the M31 GCS is generally believed to hint at a more accretion-dominated origin 
of the GCS, and may reflect a richer accretion history of M31 in comparison 
to the MW.
